Robust Agglomeration of Labeled Neurons using 3D Skeletonization

### 2017-11-05 papers/cvpr2018/3_evaluation.tex
papers: created outline for evaluation and results

@@

We evaluate our methods on EM datasets. The first dataset is the Kashtui dataset  which is a mouse brain (ADD IN STUFF) with an anisotropic resolution of $3\textrm{nm} \times 3 \textrm{nm} \times 30 \textrm{nm}$. The second dataset is from FlyEM and is a (ADD STUFF HERE) with an anisotropic resolution of $3 \textrm{nm} \times 3\textrm{nm} \times 30\textrm{nm}$.

\subsection{Preprocessing}

What percent of edges are considered.

Figure (ADD FIGURE) shows a few segments that were not considered.

@@

Here I need to produce the precision and recall curves, (ROC) as well as the final results with thresholding. Also include the training/validation loss functions overtime

\subsection{Experiments}

>>>>

We evaluate our proposed methods on two different connectomics datasets from two different species.

@@

\subsubsection{Kasthuri}

\subsubsection{FlyEM}

\subsubsection{Segmentation Pipeline and Baseline}

\subsection{Skeleton Pruning}

HOW DO WE EVALUATE THE PRUNING METHOD
HOW MANY EXAMPLES DO WE MISS

@@

HOW DO WE TRAIN THE CLASSIFIER - split the data in half and have training and validation
DATA AUGMENTATION
HOW MANY LEARNABLE PARAMETERS
WHAT NETWORKS DID WE TRY
HAVE A TABLE WITH PARAMETERS: ITERATIONS, momentum, batch size, learning rate

\subsection{Graph-based Strategies}

%We evaluate our method on two different connectomics datasets of different species.

%\subsection{Datasets}

%\subsubsection{Kasthuri}

%The first dataset is the left part of the mouse cortex volume of Kasthuri et al. (CITE). We divide the dataset into a training and validation half and a testing half. The dataset resolution is $3 \times 3 \times 30 \textrm{nm}^3/\textrm{voxel}$.

%\subsubsection{FlyEM}

%We evaluate our methods on three EM datasets. 
%TODO: Toufiq: add description of the EM datasets (volume size, resolution, type of animal, type of image scan)

%\subsubsection{NeuroProof Pipeline}
%\label{sec:neuroproof}
%Our methods build on top of existing agglomeration strategies. For the purpose of this paper we used the outputs from two established pipelines. 
%TODO: Toufiq description of neuroproof pipeline, description of FlyEM pipeline

%\subsection{Preprocessing}

%We perform significant pruning of potential merge candidates by considering only pairs of skeleton endpoints produced by Algorithm \ref{alg:generate-edges}. This strategy greatly reduced the number of false merge candidates that we considered. However, we evaluate the overall effectiveness of this strategy both in reducing trivial split candidates while maintaining a large majority of the candidates which should merge.

%Our candidate generation strategy doesn't enforce an adjacency constraint which allows us to merge candidates that are not consider under existing frameworks. We examine the success of our pipeline in merging said candidates.

%\subsection{Classifier Training}

%DISCUSS PARAMETERS FOR CLASSIFICATION

%\subsection{Graph Optimization}

%We evaluate the improvement of using a graph optimization strategy over a na\"ive approach that performs hierarchical clustering for all segments above a certain threshold.
%Using a heuristic for multicut prevents the creation of cycles. 
%Using a simple agglomeration strategy generates this many cycles.

### 2017-11-05 papers/cvpr2018/4_results.tex
papers: created outline for evaluation and results

Here we show the results for the three main contributions for this paper: merge consideration using skeleton pruning, merge probabilities output from the trained convolutional neural network, and the final output of the pipeline.

@@

\subsubsection{Finding Merge Candidates}

\subsubsection{Finding Split Candidates}

Effective pruning for merge candidates should have high precision and recall for segments that should be merged.

\subsection{Neural Network Classification}

\subsubsection{Merge Network}

@@

Figure \ref{fig:training-curve} shows the training and validation loss during the training of the neural network.

@@

\subsubsection{Split Network}

\subsection{Graph-based Error Correction}

>>>>

@@

\subsubsection{Kasthuri}

\subsubsection{FlyEM}

\subsection{Classification Performance}

\subsubsection{Kasthuri}

\subsubsection{FlyEM}

\subsection{Graph Based Strategies}

\subsubsection{Kasthuri}

\subsubsection{FlyEM}

%Here we show the results for the three main contributions for this paper: merge consideration using skeleton pruning, merge probabilities output from the trained convolutional neural network, and the final output of the pipeline.

%\subsection{Skeleton Pruning}

%\subsubsection{Finding Merge Candidates}

%\subsubsection{Finding Split Candidates}

%Effective pruning for merge candidates should have high precision and recall for segments that should be merged.

%\subsection{Neural Network Classification}

%\subsubsection{Merge Network}

@@

%Figure \ref{fig:training-curve} shows the training and validation loss during the training of the neural network.

@@

%\subsubsection{Split Network}

%\subsection{Graph-based Error Correction}
